---
title: "About data usage"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = FALSE,
  warning = FALSE,
  error = FALSE,
  comment = "#>"
)
```

To start using the data we recommend first loading the package by typing the following code into your `R` console.

```{r setup}
library(AnxietySleep)
```

Once the package is loaded, we can start calling the data under the name `anxiety`. The documentation for the data itself, as well as for each variable, can be viewed by typing `?anxiety` into your `R` console.

# Plotting the data

To visualise the data in the package, we recommend using the `ggplot2` library, which offers a whole range of functions that are driven by a common principle, the *grammar of graphs*. To get started we can load it using the `library()` function, as well as any additional packages we might need.

```{r packages}
library(ggplot2)     # Main package for graphics
library(ggside)      # For adding marginal distributions
library(ggsci)       # For wider choices on colours
```

This will allow us to generate an informative graphic that is visually pleasing.

<details><summary>See code</summary>
```{r}
# Remove extreme values 
remove_outliers <- quote(-c(which.min(pits_global), which.max(pits_global)))

fig1 <- ggplot(data = anxiety[i = eval(remove_outliers)],
       aes(x = sqrt(pits_global), 
           y = sqrt(beck_global))) +
  
  # Dot size relative to the number of observations
  geom_count(shape = 21, color = "black", aes(fill = zone), show.legend = FALSE, alpha = 0.5) +
  
  # Colour pallete from the 'New England Journal of Medicine'
  scale_color_manual(values = ggsci::pal_nejm()(2), aesthetics = c("fill", "color")) +
  
  # Adding LOESS regression line
  geom_smooth(method = "loess", se = F, aes(col = zone)) +
  
  # Adding marginal distributions
  ggside::geom_xsideboxplot(mapping = aes(y = zone, fill = zone), orientation = "y", 
                    outlier.shape = 21, outlier.alpha = .5, alpha = 0.5) +
  ggside::geom_ysideboxplot(mapping = aes(x = zone, fill = zone), orientation = "x", 
                    outlier.shape = 21, outlier.alpha = .5, alpha = 0.5) +
  
  # Removing labels from marginal distributions
  ggside::scale_xsidey_discrete(guide = guide_none()) +
  ggside::scale_ysidex_discrete(guide = guide_none()) +
  
  # Modify axis labels
  labs(x = expression(sqrt("PSQI")),
       y = expression(sqrt("BAI")),
       col = "Confinement",
       fill = "Confinement") +
  
  # Modify font size and family
  theme_linedraw(base_family = "Times",
                 base_size = 16) +
  
  # Moving legend on top and removing background grind
  theme(legend.position = "top",
        panel.grid = element_blank(),
        ggside.panel.scale.x = .15,
        ggside.panel.scale.y = (.15 * 3 / 4))
```
</details>

```{r echo=FALSE, fig.width=8, fig.height=6}
fig1
```

In this example we have recreated a figure that uses the square root of each variable as a normalisation method for the visualisation of a dot plot with three noticeable dimensions: `beck_global`, `pits_global` and the sample size relative to each dot (which is represented as the size of the dot on the graph).

Other visualisation strategies could include greater transparency for each point, which is especially useful if we have a very large sample.

# Obtaining descriptive statistics

Assuming we want to calculate the average `age` while separating the results by the `sex` and `zone` variables, we can do this with just one line of code:

```{r}
anxiety[, .(mean_age = mean(age)), .(sex, zone)]
```

The reason our syntax is so concise is because we are implicitly using the [`data.table`](https://rdatatable.gitlab.io/data.table/) package which allows us to use the `DT[i, j, by]` syntax. For more information about this package, we recommend reading its documentation.
