---
title: "Using `anxiety` dataset"
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = FALSE,
  warning = FALSE,
  error = FALSE,
  comment = "#>"
)
```

To start using the data we recommend first loading the package by typing the following code into your `R` console.

```{r setup}
library(AnxietySleep)
```

Once the package is loaded, we can start calling the data under the name `anxiety`. The documentation for the data itself, as well as for each variable, can be viewed by typing `?anxiety` into your `R` console.

## Obtaining descriptive statistics

Assuming we want to calculate the average `age` while separating the results by the `sex` and `zone` variables, we can do this with just one line of code:

```{r}
anxiety[, .(mean_age = mean(age)), .(sex, zone)]
```

The reason our syntax is so concise is because we are implicitly using the [`data.table`](https://rdatatable.gitlab.io/data.table/) package which allows us to use the `DT[i, j, by]` syntax. For more information about this package, we recommend reading its documentation.


## Plotting the data

To visualise the data in the package, we recommend using the `ggplot2` library, which offers a whole range of functions that are driven by a common principle, the *grammar of graphs*. To get started we can load it using the `library()` function, as well as any additional packages we might need.

```{r packages, message=FALSE}
library(ggplot2)     # Main package for graphics
library(ggside)      # For adding marginal distributions
library(ggsci)       # For wider choices on colours

theme_set(new = theme_classic())
```

To start with, let's create a simple bar plot comparong the mean age between men and women:

```{r}
ggplot(anxiety, aes(y  = age, x = sex)) +
  geom_bar(stat = "summary", 
           fun = "mean")
```

Nice! Now let's add some error bars representing the error of the mean to get a better intuition of the difference:

```{r}
ggplot(anxiety, aes(y  = age, x = sex)) +
  geom_bar(stat = "summary", 
           fun = "mean") +
  geom_errorbar(stat = "summary",
                fun.data = "mean_se", 
                width = .5)
```

Good, but not quite there... Maybe if we add some form of shape that can inform us about the distribution of each group. We can try using a boxplot for this end:

```{r}
ggplot(anxiety, aes(y  = age, fill = sex)) +
  geom_boxplot()
```

At this point we costumize even further by adding other geoms like violin and dots and even grouping for other variables for further enhance our work. This will allow us to generate an informative graphic that is visually pleasing:

```{r}
ggplot(anxiety, aes(y  = age, x = sex, fill = zone)) +
  facet_grid(cols = vars(zone)) +
  geom_violin(alpha = 0.3) +
  geom_boxplot(width = 0.1, outlier.shape = NA) +
  geom_jitter(cex = 1, width = .1, alpha = 0.2) +
  labs(fill = "Confinement zone", x = "Sex", y = "Age (years old)",
       title = "Age by Sex and Confinement Zone",
       subtitle = "Violin and box plots showing the observed age distribution per group",
       caption = "CZ = Confinement zone\nUZ = Unconfinement zone")
```

By using a layer-style plotting system, we can create informative visualization that can generate meaningfull insights from the data.
